Hypertension and microbiome

### 2019-02-26 articletwo.Rmd
Minor

```{r matrix calculation}
if (!file.exists("rds/bray.dist.m.species.rds") || !file.exists("rds/bray.dist.m.genus.rds")) {
    bray.dist.m.species <- calculate.beta.matrix(pseq.species)
    saveRDS(bray.dist.m.species, file = "rds/bray.dist.m.species.rds")
} else {
    bray.dist.m.species  <- readRDS("rds/bray.dist.m.species.rds")
}
```

@@

```{r Write figure 5}
fig4head <- "P2"
fig4foot <- ""
writeimage(doc, 4, "cache/pca.p2.png", fig4head, fig4foot)
```

@@

>>>>

```{r matrix calculation}
if (!file.exists("rds/bray.dist.m.species.rds")) {
    bray.dist.m.species <- calculate.beta.matrix(pseq.species)
    saveRDS(bray.dist.m.species, file = "rds/bray.dist.m.species.rds")
} else {
    bray.dist.m.species  <- readRDS("rds/bray.dist.m.species.rds")
}
```

@@

```{r Write figure 4}
fig4head <- "P2"
fig4foot <- ""
writeimage(doc, 4, "cache/pca.p2.png", fig4head, fig4foot)
```

@@

```{r save session}
save.session(paste0("cache/session-", now, ".Rda"))
```
